A Sound and Complete Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2025-08-20 paper/COLA/paper.tex
List our axioms

>>>>

Every result stated has been fully checked. We note, though, that the
completeness result (Section \ref{sec:completeness}) relies on the excluded
middle as an additional axiom, given that our completeness proof is fully classical;
we also axiomatize that formulas (defined below) are countable, and leave as
future work to properly demonstrate this.
